---
title: "p8105_hw1_jr4392"
author: "Junyi Ren"
date: "2023-09-22"
output: github_document
---


```{r}
library(moderndive)
library(tidyverse)
```

## Problem 1

```{r}
data("early_january_weather")
```

The dataset has 15 variables: origin(weather station)/EWR, year/2013, month/1, day/1-15, hour(recorded time)/0-23, temp/temperature in F, dewp/dew point in F, humidity/0-100, wind_dir/wind direction in degrees 0-360, wind_speed/wind speed in mph, precip/precipitation in inches, pressure/sea level pressure in millibars, visib/visibility in miles, and time_hour/recorded date and hour.
The dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. 
The mean temperature is `r mean(early_january_weather$temp)`F.

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("problem 1 scatterplot.png")
```
In this plot, the temperature increased as the day went on. On days with high humidity, the temperature does not change much.

## Problem 2

```{r}
P2_df = 
  tibble(
    ran_sam = rnorm(10),
    log_vec = ran_sam > 0,
    cha_vec = as.character(c("a","b","c","d","e","f","g","h","i","j")),
    fac_vec = factor(c("L1","L2","L3","L1","L2","L3","L1","L2","L3","L1"),
                     levels = c("L1","L2","L3"))
    )
```

```{r}
mean(pull(P2_df,var=1))
mean(pull(P2_df,var=2))
mean(pull(P2_df,var=3))
mean(pull(P2_df,var=4))
```

The first and second column can take the mean, which are numeric and logical columns. The last two column cannot take the mean,  character and factor cannot take the mean.

```{r, eval=FALSE}
as.numeric(pull(P2_df,var=2))
as.numeric(pull(P2_df,var=3))
as.numeric(pull(P2_df,var=4))
```

Logical vector can be converted to numeric values, 1 for true and 0 for false, so the logical vector has a mean.Character vector cannot be converted to numbers.Letters in a character vector do not have numerical meanings, so there are no numbers to represent these characters, and no mean.The numerical values of the factor vector show the levels from 1 to 3. There is no mean for the level values because it is meaningless.
